\plaintitle

### 2016-12-13 drafts/labor/complexity.tex
piecework literature review section mostly updated. the various research questions might still be a bit of a mess

\subsubsection{\crowdworkpers}

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless crowdsourcing can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers~\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling~\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants \cite{lasecki2013chorus},
medical data interpreters \cite{lasecki2013chorus}, and
idea generation workflows \cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing workflows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce~\cite{crowdForgeKittur} or
sequence alignment algorithms~\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
% \ali{We could quote \citeauthor{storiesIraniSilberman} and say ``human APIs'',
% but that gets a little critique--y, and we might want to save that for later.}
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

It is now clear that this computational workflow approach works with focused complex tasks, but
the broader wicked problems largely remain unsolved~\cite{rittel1973dilemmas}.
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,
      writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering \cite{chilton2013cascade},
categorization \cite{andre2014crowd}, and
outlining \cite{luther2015crowdlines}
are possible, but there is no general solution for sensemaking.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.
%  and
% other crowdsourced goals such as addressing climate change
% \cite{introne2011climate}.

Restricting attention to non--expert, microtask workers proved limiting.
So, \citeauthor{foundry} introduced the idea of crowdsourcing with
online paid \textit{experts} from platforms such as Upwork.
Expert crowdsourcing enables access to a much broader set of workers,
for example designers and programmers.
The same ideas can then be applied to expert ``macro--tasks''~\cite{cheng2015break,haas2015argonaut}, enabling the crowdsourcing of goals such as user--centered design \cite{foundry},
programming \cite{latoza2014microtask,Fast2016,Chen2016}, and
mentorship \cite{suzukiAtelier}.
However, there remains the open question of
how complex the work outcomes from expert crowds can be.

\subsubsection{\pieceworkpers}

@@

\topic{\citeauthor{grier2013computers} gives early accounts of
a piecework strategy in Airy's creation of
the British Nautical Almanac~\cite{grier2013computers}.}
Airy's goal was complex
--- mathematical calculations to produce tables that would
allow sailors to locate themselves by starlight from sea.
Many of his contributors did not have high--level mathematical training,
so Airy broke down the task into simpler calculations and
distributed them by mail,
accomplishing the complex goal through piecework tasks that paid little.

However, when piecework entered the American economy,
it was not used for complex work.
One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage \cite{burton1899commercial} and
management regimes \cite{norton1900textile}
rather than training.

Measurement also limited the complexity of piecework:
only tasks that could be measured and priced could be completed via piecework. 
When \citeauthor{Brown01041990} investigated
what limited the adoption of piecework in industries that otherwise gravitated toward it
(e.g., railway engineers),
the homogeneity of tasks arose as a major contributing factor~\cite{Brown01041990}.
\citeauthor{10.2307/23702539} concurs via a case study of the Santa Fe Railway,
which used ``efficiency experts'' to develop a ``standard time''
to determine pay for each task at the company informed by
``thousands of individual operations''% removed ``at the Topeka shop'' because even I had to reach back into the back of my mind to be like ``Oh, yeah, Kansas''.
~\cite{10.2307/23702539}.
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work
--- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.

@@

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} were amenable to piecework.}
Researchers detail three organizational criteria.
First, \citeauthor{Brown01041990} argues that
piecework ``is less likely in jobs with a variety of duties than in
jobs with a narrow set of routinized duties''~\cite{Brown01041990}.
\citeauthor{SJOE:SJOE371} points out the phenomenon here as a market effect:
``in an environment with multi--tasking,
pay schemes based on tightly specified performance may
induce workers to neglect tasks that are less easy to measure''~\cite{SJOE:SJOE371}.
Second,
complexity was limited by access to capital to create the necessary infrastructure.
As \citeauthor{10.2307/23702539} reports,
only the largest and most wealthy railroads had the resources
necessary
% ``pay the overhead involved in installing work reorganization''
~\cite{10.2307/23702539}.
Third, organizations required capable managers in charge of the pieceworkers.
The West Virginia mines, for example, hired foremen 
to be the intermediary between upper management and the workers~\cite{10.2307/2118435}.
These foremen were responsible for allocating resources and
understanding when and how to modify work as necessary~\cite{wray1949marginal}.
So, in sum,
organizations historically could only take advantage of piecework if they had
homogeneous work to be done,
access to capital to purchase the necessary equipment, and
the ability to hire people who could serve as intermediaries between pieceworkers and management.

@@

\subsubsection{\whatchanged}
\begin{comment}
  mangeerial overhead limits, so what's different
  more people can now do complex work without training (more complex)
  parts of management can be automated (more firms)
  cheaper to create the infrastructure (more complex)
\end{comment}
% \topic{Piecework makes a number of observations leading to the conclusion that
% piecework's complexity is fundamentally bounded by several limitations,
% chief among them the costs of managerial overhead and the transition thereto.}
% \citeauthor{Brown01041990} and \citeauthor{10.2307/23702539}'s claims that
% organizations can't adopt piecework unless
% they're sufficiently large to absorb the cost of transitioning to a piecework system;
% \citeauthor{10.2307/2118435} and \citeauthor{wray1949marginal}'s observations for
% the importance of competent, effective managerial oversight
% --- a human resource, which made the scaling cost prohibitively expensive for many
% \cite{10.2307/2118435,wray1949marginal,10.2307/23702539,Brown01041990}.

% \topic{Digital media have expanded the scope of
% viable piecework by pushing drastically on the limits
% cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity~\cite{Brown01041990}.
Given the flourishing of on--demand labor platforms such as
Uber, AMT, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the internet has trivialized
the costs and challenges of the earlier limiting factors
because technology makes it easier
\begin{inlinelist}
\item for workers to do complex work without training,
\item to manage workers in doing complex work, and 
\item to create the infrastructure necessary to manage the workers.
\end{inlinelist}

@@

% \ali{maybe this should go away?
% \topic{Technology has made it possible
% for non--experts to do work that was once considered
% within the domain of experts.}
% \citeauthor{yuanAlmost} builds on the work of others
% (\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
% to design workflows that yield ``expert--level feedback''
% \cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
% This body of work identifies ways to transform a variety of duties comprising complex tasks
% and distills them into ``a narrow set of routinized duties'',
% informed in part by researchers --- acting as inspectors --- and experts
% \cite[quotations from][]{10.2307/23702539}.
% Where \citeauthor{10.2307/23702539} would call additionally for the identification of
% crowdsourcing's version of ``piecework clerks'', we point out that
% today algorithms manage workers as pieceworkers once did
% \cite{uberAlgorithm,10.2307/23702539}.}
Finally, the organizational limit on infrastructure creation is somewhat lessened. Writing web scripts takes fewer people and fewer hours than creating physical equipment for piecework.
\citeauthor{turkitLittle}'s vision was that any user with basic programming skills could tap into on--demand human intelligence.
As better toolkits lower this threshold~\cite{myers2000past} and computational thinking diffuses, a broader population will be able to use crowd work.

\subsubsection{\implication}
% \topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
% it also signals some of the ultimate limitations of crowd work and piecework in general.}
% While the threshold preventing task requesters from utilizing piecework
% has dropped thanks to affordances of the internet, the ceiling on task complexity hasn't moved significantly.
% \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
% If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
% we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation \cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework \cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors~\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing--complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
%At worst, as now, they are far simpler~\cite{uberAlgorithm}.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per--person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to afford crowd work.
This shift may enable complex goals that were not cost--effective before to become feasible.
However, because algorithms remain far from replicating all of the foremen's responsibilities, most likely is a middle ground in which crowd work re--introduces the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters \cite{MaliciousCrowdworkersGadiraju}.
% and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
% \cite{takingAHITMcInnis}.
% \ali{What will happen if we don't do this?
% Maybe this is where I should bring up
% the ``market for lemons'' metaphor and say that
% the market will just continue to decline in quality until
% nobody is willing to rely on it either as a source of data/information (requesters), or
% a means of sustaining oneself financially (workers).}

>>>>

\onlyinsubfile{\newpage}
\subsubsection{\crowdworkpers}

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless crowdsourcing can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers~\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling~\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation workflows~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing workflows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce~\cite{crowdForgeKittur} or
sequence alignment algorithms~\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

It is now clear that this computational workflow approach works with focused complex tasks, but
the broader wicked problems largely remain unsolved~\cite{rittel1973dilemmas}.
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering~\cite{chilton2013cascade},
categorization~\cite{andre2014crowd}, and
outlining~\cite{luther2015crowdlines}
are possible, but there is no general solution for sensemaking.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.

Restricting attention to non--expert, microtask workers proved limiting.
So, \citeauthor{foundry} introduced the idea of crowdsourcing with
online paid \textit{experts} from platforms such as Upwork.
Expert crowdsourcing enables access to a much broader set of workers,
for example designers and programmers.
The same ideas can then be applied to expert ``macro--tasks''~\cite{cheng2015break,haas2015argonaut}, enabling the crowdsourcing of goals such as user--centered design~\cite{foundry},
programming~\cite{latoza2014microtask,Fast2016,Chen2016}, and
mentorship~\cite{suzukiAtelier}.
However, there remains the open question of
how complex the work outcomes from expert crowds can be.

\onlyinsubfile{\newpage}
\subsubsection{\pieceworkpers}

@@

\ali{I'm not sure that this really stays close to the three case studies that emerged as major threads (now in the piecework lit review).
Should I refactor/rewrite this to make it more relevant?}
Measurement also limited the complexity of piecework:
only tasks that could be measured and priced could be completed via piecework. 
When \citeauthor{Brown01041990} investigated
what limited the adoption of piecework in industries that otherwise gravitated toward it
(e.g., railway engineers),
the homogeneity of tasks arose as a major contributing factor~\cite{Brown01041990}.
\citeauthor{10.2307/23702539} concurs via a case study of the Santa Fe Railway,
which used ``efficiency experts'' to develop a ``standard time''
to determine pay for each task at the company informed by
``thousands of individual operations''% removed ``at the Topeka shop'' because even I had to reach back into the back of my mind to be like ``Oh, yeah, Kansas''.
~\cite{10.2307/23702539}.
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work
--- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.

@@

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} were amenable to piecework.}
Researchers detail three organizational criteria.
\begin{Numberlist}
\item \citeauthor{Brown01041990} argues that
piecework ``is less likely in jobs with a variety of duties than in
jobs with a narrow set of routinized duties''~\cite{Brown01041990}.
\citeauthor{SJOE:SJOE371} points out the phenomenon here as a market effect:
``in an environment with multi--tasking,
pay schemes based on tightly specified performance may
induce workers to neglect tasks that are less easy to measure''~\cite{SJOE:SJOE371}.
\item complexity was limited by access to capital to create the necessary infrastructure.
As \citeauthor{10.2307/23702539} reports,
only the largest and most wealthy railroads had the resources
necessary
% ``pay the overhead involved in installing work reorganization''
~\cite{10.2307/23702539}.
\item organizations required capable managers in charge of the pieceworkers.
The West Virginia mines, for example, hired foremen 
to be the intermediary between upper management and the workers~\cite{10.2307/2118435}.
These foremen were responsible for allocating resources and
understanding when and how to modify work as necessary~\cite{wray1949marginal}.
\end{Numberlist}
So, in sum,
organizations historically could only take advantage of piecework if they had
homogeneous work to be done,
access to capital to purchase the necessary equipment, and
the ability to hire people who could serve as intermediaries between pieceworkers and management.

@@

\onlyinsubfile{\newpage}
\subsubsection{\whatchanged}
\begin{comment}
  mangeerial overhead limits, so what's different
  more people can now do complex work without training (more complex)
  parts of management can be automated (more firms)
  cheaper to create the infrastructure (more complex)
\end{comment}

The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity~\cite{Brown01041990}.
Given the flourishing of on--demand labor platforms such as
Uber, AMT, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the internet has trivialized
the costs and challenges of the earlier limiting factors
because technology makes it easier
\begin{inlinelist}
\item for workers to do complex work without training,
\item to manage workers in doing complex work, and 
\item to create the infrastructure necessary to manage the workers.
\end{inlinelist}

@@

Finally, the organizational limit on infrastructure creation is somewhat lessened. Writing web scripts takes fewer people and fewer hours than creating physical equipment for piecework.
\citeauthor{turkitLittle}'s vision was that any user with basic programming skills could tap into on--demand human intelligence.
As better toolkits lower this threshold~\cite{myers2000past} and computational thinking diffuses, a broader population will be able to use crowd work.

\subsubsection{\implication}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation~\cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework~\cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors~\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing--complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per--person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to afford crowd work.
This shift may enable complex goals that were not cost--effective before to become feasible.
However, because algorithms remain far from replicating all of the foremen's responsibilities, most likely is a middle ground in which crowd work re--introduces the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters~\cite{MaliciousCrowdworkersGadiraju}.

### 2016-12-13 drafts/labor/decomposition.tex
piecework literature review section mostly updated. the various research questions might still be a bit of a mess

\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work
consist of creative methods for decomposing goals.}
Even when tasks such as writing and editing cannot be reliably performed by individual workers,
researchers demonstrated that
decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,
                                                               bernsteinSoylent,
                                                               writingMicroTasks,
                                                               Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows,
which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g.,
a paragraph topic~\cite{crowdForgeKittur},
an error~\cite{bernsteinSoylent},
or a concept~\cite{Yu2016a,Yu2016b} and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas,
including food labeling~\cite{noronha2011platemate},
brainstorming~\cite{siangliulue2015toward,yu2014distributed},
and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

@@

\subsubsection{\pieceworkpers}
\citeauthor{Brown01041990} inquired from another direction,
asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined,
this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically,
the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework~\cite{Brown01041990}.

\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories,
but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter'',
an icon of \nth{20} century America who
represented empowerment and opportunity for women \cite{honey1985creating},
was a pieceworker~\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First,
work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second,
tasks were discrete
--- that is,
independent from one another.
Finally,
workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers,
but certainly in Ford and Taylor's time,
highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result,
the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

@@

\subsubsection{\whatchanged}
\begin{comment}
outline
	- measurement is more precise,
  so decomposition is deeper
	- not a single position,
  but a marketplace
\end{comment}

\topic{Where measurement and instrumentation were limiting factors for historical piecework,
computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable,
but trivial~\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
% cites as
preventing scientific management from being fully utilized,
%the difficulty of tracking work \& workers,
no longer exists
%\cite{10.2307/23702539}.}
modern crowd work is measuring and modeling every click,
scroll,
and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled,
edited,
and redeployed~\cite{hu1961parallel}.
In contrast,
today system--designers can share,
modify,
and instantiate environments
like sites of labor in a few lines of code~\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions,
and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago~\cite{dai2015and,
                                                              Cai:2016:CRI:2858036.2858237,
                                                              cheng2015break,
                                                              measuringCrowdsourcingCheng,
                                                              embracingErrorKrishna}.

@@

\subsubsection{\implication}
If measurement precision limited the depth of decomposition for piecework historically,
as \citeauthor{10.2307/23702539} argues,
then modern on--demand work stands to become far more finely--sliced and highly decomposed than ever before.
Online tools make measurement and validation so easy~\cite{rzeszotarski2011instrumenting} that these aspects of piecework are solved,
or near enough that they no longer limit task decomposition.
Now,
not just tasks,
but entire workers' histories~\cite{hata2017glimpse},
can be collected and analyzed in detail.

However,
decomposition has hit a second bottleneck: cognition. 
Task switching costs and other cognitive costs make it difficult
to work on tasks so far decontextualized from their original intention \cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context,
and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context
--- for example,
logo design requires a deep understanding of the client and their goals.
In part due to this limitation,
99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

@@

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }

>>>>

\onlyinsubfile{\newpage}
\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work
consist of creative methods for decomposing goals.}
Even when tasks such as writing and editing cannot be reliably performed by individual workers,
researchers demonstrated that
decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,
                                                               bernsteinSoylent,
                                                               writingMicroTasks,
                                                               Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows,
which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g.,
a paragraph topic~\cite{crowdForgeKittur},
an error~\cite{bernsteinSoylent},
or a concept~\cite{Yu2016a,Yu2016b} and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas,
including food labeling~\cite{noronha2011platemate},
brainstorming~\cite{siangliulue2015toward,yu2014distributed},
and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

@@

\onlyinsubfile{\newpage}
\subsubsection{\pieceworkpers}
\citeauthor{Brown01041990} inquired from another direction,
asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined,
this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically,
the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework~\cite{Brown01041990}.

\ali{This can be trimmed to just reference back to the piecework review}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for the better part of a century.}
The beginnings of
systematic task decomposition 
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
\begin{Numberlist}
\item work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
\item tasks were discrete
--- that is,
independent from one another.
\item workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.
\end{Numberlist}

@@

\onlyinsubfile{\newpage}
\subsubsection{\whatchanged}
\begin{comment}
outline
	- measurement is more precise,
  so decomposition is deeper
	- not a single position,
  but a marketplace
\end{comment}

\topic{Where measurement and instrumentation were limiting factors for historical piecework,
computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable,
but trivial~\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
preventing scientific management from being fully utilized,
no longer exists
modern crowd work is measuring and modeling every click,
scroll,
and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled,
edited,
and redeployed~\cite{hu1961parallel}.
In contrast,
today system--designers can share,
modify,
and instantiate environments
like sites of labor in a few lines of code~\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions,
and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago~\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

\onlyinsubfile{\newpage}
\subsubsection{\implication}
If measurement precision limited the depth of decomposition for piecework historically,
as \citeauthor{10.2307/23702539} argues,
then modern on--demand work stands to become far more finely--sliced and highly decomposed than ever before.
Online tools make measurement and validation so easy~\cite{rzeszotarski2011instrumenting} that these aspects of piecework are solved,
or near enough that they no longer limit task decomposition.
Now,
not just tasks,
but entire workers' histories~\cite{hata2017glimpse},
can be collected and analyzed in detail.

However,
decomposition has hit a second bottleneck: cognition. 
Task switching costs and other cognitive costs make it difficult
to work on tasks so far decontextualized from their original intention~\cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context,
and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context
--- for example,
logo design requires a deep understanding of the client and their goals.
In part due to this limitation,
99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
}
